Kids stove grades and usage summary

### 2020-05-14 demographics_summary.Rmd
summary stat updates

```{r}
# summary data for manuscript tables
demo_funct_total <- function(var, data = demographics_initial){

@@

demo_funct_total("gender_parent")
demo_funct_total("hispanic_parent")
demo_funct_total("race_parent")

demo_funct_area <- function(var, data = demographics_initial){

@@

demo_funct_area("gender_parent")
demo_funct_area("hispanic_parent")
demo_funct_area("race_parent")
```

>>>>

```{r}
# summary data for manuscript tables
char_funct_total <- function(var, data = demographics_initial){

@@

char_funct_total("gender_parent")
char_funct_total("hispanic_parent")
char_funct_total("race_parent")

char_funct_area <- function(var, data = demographics_initial){

@@

char_funct_area("gender_parent")
char_funct_area("hispanic_parent")
char_funct_area("race_parent")
```

### 2020-05-14 manuscript_tables_figures.Rmd
summary stat updates

@@

sums_rolling_pm_data <- 
  read_rds(paste0(file_path, "Output/sums_rolling_pm_data.rds"))

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds"))
```

@@

```{r}
# add new vars to dataset

```

```{r}
# summary data for manuscript tables
demo_funct_total <- function(var, data = health_exposure_data_sampling_day){

@@

demo_funct_area <- function(var, data = health_exposure_data_sampling_day){

@@

demo_funct_total("gender_parent")
demo_funct_area("gender_parent")
demo_funct_total("hispanic_parent")
demo_funct_area("hispanic_parent")
demo_funct_total("race_parent")
demo_funct_area("race_parent")
demo_funct_total("education_3level")
demo_funct_area("education_3level")
demo_funct_total("income_3level")
demo_funct_area("income_3level")
```

>>>>

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds"))

@@

sums_rolling_pm_data <- 
  read_rds(paste0(file_path, "Output/sums_rolling_pm_data.rds"))
```

@@

```{r}
# add new vars to dataset
checkdata <- health_exposure_data_sampling_day %>% 
  select(area, home, residents_under_five)
```

```{r}
# summary data for manuscript tables
char_funct_total <- function(var, data = health_exposure_data_sampling_day){

@@

char_funct_area <- function(var, data = health_exposure_data_sampling_day){

@@

char_funct_total("gender_parent")
char_funct_area("gender_parent")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_parent")
char_funct_area("race_parent")
char_funct_total("education_3level")
char_funct_area("education_3level")
char_funct_total("income_3level")
char_funct_area("income_3level")
char_funct_total("home_floors_2level")
char_funct_area("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_area("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_area("home_pets_2level")
char_funct_total("stove_age_3level")
char_funct_area("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_area("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_area("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_area("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_area("stove_grade_3level")
```

```{r}
# summary data for manuscript tables
num_funct_total <- function(var, data = health_exposure_data_sampling_day){

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

num_funct_area <- function(var, data = health_exposure_data_sampling_day){

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  select(area, home, new_var) %>% 
  group_by(area) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

num_funct_total("residents_under_five")
num_funct_area("residents_under_five")
num_funct_total("home_bedrooms")
num_funct_area("home_bedrooms")
```

### 2020-05-14 stove_grade_usage_summary.Rmd
summary stat updates

```{r}
# Load data
stove_grades_clean <- read_rds("Output/stove_grades_clean.rds") 
stove_use_clean <- read_rds("Output/stove_use_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds") 
demographics_clean <- read_rds("Output/demographics_clean.rds")
#pm_clean <- read_rds("Output/pm_clean.rds")
```

>>>>

```{r}
# Load data
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

stove_grades_clean <- read_rds(paste0(file_path, "Output/stove_grades_clean.rds")) 
stove_use_clean <- read_rds(paste0(file_path, "Output/stove_use_clean.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))
demographics_clean <- read_rds(paste0(file_path, "Output/demographics_clean.rds"))
#pm_clean <- read_rds(paste0(file_path, "Output/pm_clean.rds"))
```
